Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-16 writeup/gz_hubble_data.tex
swap S3.1 and 3.2; add S3 intro
closes #96; also addresses one of the points on Carie's list in #109

\documentclass[twocolumn]{aastex6}

@@

The votes of individual classifiers in GZH were combined to make a vote
fraction for each response ($f_{response}$) to a question in the classification
tree. Votes were weighted in a method similar that in previous versions of
Galaxy~Zoo \citep{lan08,wil13}, such that classifiers who frequently disagreed
with others ended up having very low weights. The weighting $(w)$ was 1 for the
top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
classifiers, $w$ was designed to drop smoothly and was effectively zero for the
bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
an even smaller percentage of the classifications) the overall effect on the
GZH dataset was minimal. The method was effective, however, at filtering out
contributions from random or deliberately malicious classifiers.

Classifications were aggregated and weighted only if the classifier was logged
into GZH under their username (which was encouraged, but not required for
participation). Classifications by participants who were not logged in were marked as
``Anonymous''; no weighting was applied, but the data were otherwise treated
identically in the data processing.

@@

The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS,
GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
simulated AGN were activated in Dec 2010, as well as a small sample of
AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on
an overly restrictive cut on blended and/or saturated objects. The main GZH
site collected data until its replacement, the fourth phase of
Galaxy~Zoo\footnote{\url{http://zoo4.galaxyzoo.org}} (including data from both
the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 on
the fourth version of the Galaxy~Zoo site. The GZH project had a total of
10,349,357~classifications from 93,898 registered participants. 
% Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.

>>>>

\documentclass[twocolumn]{aastex}

@@

Below we describe the classification structure of GZH, including the software 
interface and the hierarchical structure of a classification. Section \ref{ssec:weighting}
describes the process of combining individual classifications into vote fractions for each
galaxy.

@@

The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS,
GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
simulated AGN were activated in Dec 2010, as well as a small sample of
images from AEGIS, GEMS, and GOODS that were previously excluded from the original sample
due to cuts on blended and/or saturated objects and subsequently confirmed as classifiable galaxies. The main GZH
site collected data until its replacement, the fourth phase of
Galaxy~Zoo\footnote{\url{http://zoo4.galaxyzoo.org}} (including data from both
the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 on
the fourth version of the Galaxy~Zoo site. The GZH project had a total of
10,349,357~classifications from 93,898 registered participants. 
% Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.

As a first step to producing consensus classifications of each galaxy, 
the votes of individual classifiers in GZH were combined to make a vote
fraction for each response ($f_{response}$) to a question in the classification
tree. Votes were subsequently weighted and re-combined in an iterative method similar that in 
previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a method chosen 
to be as egalitarian as possible while also identifying and downweighting classifiers 
who frequently disagreed with others. The weighting factor $(w)$ was 1 for the
top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
classifiers, $w$ was designed to drop smoothly and was effectively zero for the
bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
% would be good to quantify "tiny" and "even smaller [than tiny]"
an even smaller percentage of the classifications) the overall effect on the
GZH dataset was minimal. The method was effective, however, at filtering out
contributions from random or deliberately malicious classifiers.

Classifications were aggregated and weighted only if the classifier was logged
into GZH under their username (which was encouraged, but not required for
participation). Classifications by participants who were not logged in were marked as
``Anonymous'' and assumed to have $w = 1$. 
% We should also try to estimate how many anonymous classifiers there were, if possible.
